Universal relations after GW170817

### 2018-11-16 paper/bin-love-after-gw170817.tex
updates to paper draft

%Final Results
Upon use of the constrained set of EoSs, we find an improvement in binary Love universality by a factor of 25\% for stars with mass below 1.7 solar masses, and in I-Love-Q universality by a factor of 22\%.
Unfortunately, due to the current limitations in detector sensitivity, the systematic errors arising from EoS variation in the universal relations are far outweighed by the statistical errors accrued by extraction of high-order PN tidal parameters from GW waveforms.
Fig.~\ref{fig:stackedFisher} compiles the results from Fisher analyses approximating the uncertainties accrued from parameter extraction for GW170817 as if it had been observed by future detectors aLIGO, a\texttt{++}, Voyager, ET, and CE\zc{cite these individually}.
Here, $\sigma_1$ corresponds to the statistical error found from observing GW170817, and $\sigma_N$ represents the combined uncertainty after the detection of $N$ events (corresponding to the binary NS merger rate associated with each interferometer).
These values are further tabulated in Table~\ref{tab:variances}.
It can be seen from this figure that the statistical errors from parameter extraction become comparable the universal relation systematics (indicated by the magenta horizontal line) for the Voyager telescope - indicating when improved binary Love universal relations will become viable.
\begin{figure}
\begin{center} 
\includegraphics[width=\columnwidth]{stackedFisher.pdf}
\end{center}
\caption{
\zc{Redo this image in xmgrace.}
Estimated statistical uncertainties $\sigma_1$ (blue) in the extraction of $\tilde{\Lambda}$ from GW170817 (O2) as if it were observed with future interferometers aLIGO, a++, Voyager, CE, and ET as a function of SNR.
This is compared to the combined uncertainty $\sigma_N$ (orange) from the observation of multiple events from a simulated population of size $N$ corresponding to the expected rate of binary NS observations for O2, aLIGO, a\texttt{++}, Voyager, CE, and ET over 2 observing runs: 2, 44, 355, 4818, 256620, and 1349917 respectively.
It can be seen that the statistical errors in parameter extraction become comparable to the systematics from EoS variation in binary Love relations (magenta) for Voyager and on.
Note the approximation for $\sigma_N$ under the O2 detector sensitivity is a poor estimate due to the small number of stacked events, $N_{\text{O2}}=2$, resulting in a high degree of randomness in population generation.
These results are further tabulated in Table~\ref{tab:variances}.
}
\label{fig:stackedFisher}
\end{figure}

@@

In the current analysis, we consider only EoSs which have been constrained by the recent binary neutron star merger event, GW170817.
Important recent work~\cite{LIGO:posterior} uniformly sampled EoS parameters in order to derive a marginalized posterior on the pressure as a function of mass density, as seen in Fig. 2 of~\cite{LIGO:posterior}.
In our work, we similarly sample spectral coefficients within the ranges: $\gamma_0 \in \lbrack 0.2,2 \rbrack$, $\gamma_1 \in \lbrack -1.6,1.7 \rbrack$, $\gamma_2 \in \lbrack -0.6,0.6 \rbrack$, $\gamma_0 \in \lbrack -0.02,0.02 \rbrack$, and further restricting the adiabatic index to be $\Gamma \in \lbrack 0.6,4.5 \rbrack$, ensuring our parameterization exposes a wide range of viable EoSs~\cite{Lindblom:parameters}.
In addition, we impose similar constraints as was done in~\cite{LIGO:posterior}: (i) causality within 10\%, and (ii) EoS priors must support NS masses up to $1.97 \text{ M}_{\odot}$, consistent with astrophysical observations.
We then utilize the posterior defined by GW170817 by rejecting any EoS sample which does not lie within the 90\% credible posterior region, resulting in a sample of 35 EoSs shown in Fig.~\ref{fig:eos}.
Following~\cite{Read2009}, the parameterized high-density core EoSs generated above are matched to the low-density crust EoS Sly~\cite{Douchin:2001sv} at the density such that the pressures are equal.
For comparison, we also include a second sample of randomly generated EoSs, without restricting to GW170817s posterior.
\begin{figure}
\begin{center} 
\includegraphics[width=\columnwidth]{EoSs.pdf}
\end{center}
\caption{
\zc{Redo this image in xmgrace.}Set of 35 randomly generated EoSs used in our analysis. 
These were populated by uniformly sampling the spectral coefficient parameter space, then restricting to the 90\% credible level on EoS as derived by~\cite{LIGO:posterior}.
}
\label{fig:eos}
\end{figure}

\subsection{Tidal deformability}\label{tidal}
Binary neutron star mergers, such as GW170817, provide valuable insight into the internal structure of such stars. 
Namely, tidal effects which enter the gravitational waveform depend strongly on the EoS defining the NSs structure. 
The ($l=2$ electric type) \emph{tidal deformability}, denoted as $\lambda$, has the largest impact on the waveform phase. 
Consider a NS of mass $M$ in the presence of the tidal field $\varepsilon_{ij}$ of a companion star.
In response, the NS will deform away from sphericity under the aquisition of quadrupole moment $Q_{ij}$, characterized by $\lambda$ as the linear response to $\varepsilon_{ij}$~\cite{Flanagan2008,hinderer-love,Yagi2013}:
\begin{equation}
Q_{ij}=-\lambda \varepsilon_{ij}.
\end{equation}
One can extract $\lambda$, or its dimensionless form $\Lambda \equiv \lambda/M^5$, via different asymptotic limits of the gravitational potential:
\begin{align}
\begin{split}
\Phi=\frac{1+g_{tt}}{2}&=-\frac{M}{r} - \frac{3}{2}\frac{Q_{ij}}{r^3} \Bigg(\frac{x^i}{r} \frac{x^j}{r}-\frac{1}{3}\delta_{ij} \Bigg) + \mathcal{O} \Bigg( \frac{M^4}{r^4} \Bigg)\\
&+ \frac{1}{2} \varepsilon_{ij} x^i x^j + \mathcal{O} \Bigg( \frac{r^3}{M^3} \Bigg).
\end{split}
\end{align}
This process is described in more detail in~\cite{hinderer-love}.

Next, we consider the case of two NSs in a binary, such as the system found in GW170817, where each star 
individually experiences a neighboring tidal field.
Thus each star possesses tidal deformabilities $\Lambda_1$ and $\Lambda_2$ entering the gravitational waveform.
Due to strong correlations between these parameters, individual extraction is very difficult with current interferometer sensitivity limitations.
However, the waveform templates can be strategically reparameterized to instead include independant linear combinations of $\Lambda_1$ and $\Lambda_2$ to mitigate correlations between them. 
Any set of two independent functions may be used, for example: tidal parameters $\tilde{\Lambda}=\tilde{\Lambda}(\Lambda_1,\Lambda_2)$ and $\delta \tilde{\Lambda}=\delta \tilde{\Lambda}(\Lambda_1,\Lambda_2)$ enter the gravitational waveform at 5PN and 6PN orders respectively, thus partially breaking degeneracies.
Here, $\tilde{\Lambda}$ is the weighted average tidal deformability, or chirp deformability due to its status as the primary tidal parameter in the waveform.

@@

\subsection{I-Love-Q relations}\label{sec:ilq}
Here we present our results on I-Love-Q universality as compared to Fig. 1 of Yagi \textit{et al.}~\cite{Yagi:ILQ}.
Following this work, the data for each universal relation is fit to the following curve:
\begin{equation}\label{eq:ILQfit}
\ln{y_i}=a+b \ln{x_i} + c (\ln{x_i})^2 + d (\ln{x_i})^3 + e (\ln{x_i})^4,
\end{equation}
where the updated coefficients are given in Table~\ref{tab:ILQfit}.
In particular, we focus only on the I-Love universal relation for brevity, noting that the remaining relations Q-Love and I-Q show similar results.

@@

%%%%%%%%%%%%%%%%%%%%%%%%% Begin Future Observations %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Impact on future observations}\label{sec:observations}
In this section, we estimate the feasibility of ultilizing improved universal relations in future binary NS merger events.
This estimate is aqcuired through a simple Fisher analysis~\cite{Finn:Fisher,Cutler:Fisher} which approximates the accuracy with which one can extract best-fit parameters $\theta^a$, given a prior template waveform.
For the remainder of the paper, we consider a template parameter vector consisting of:
\begin{equation}
\theta^a=(\ln{A},\phi_c,t_c,\ln{\mathcal{M}},\ln{\mathcal{\eta}},\chi_s,\chi_a,\tilde{\Lambda},\delta \tilde{\Lambda}),
\end{equation}
where $A \equiv \sqrt{\frac{2 \eta}{3 \pi^{1/3}}}$ is a normalized amplitude factor, $\eta \equiv m_1 m_2/M^2$ is the symmetric mass ratio with $m_{1,2}$ and $M$ being the individual and total masses, $\mathcal{M}=M \eta^{3/5}$ is the chirp mass, and $\chi_{s,a}=\frac{1}{2}(\chi_1+\pm\chi_2)$ are the symmetric and antisymmetric total spins, where $\chi_{1,2}$ are the NSs individual spins. 
Following Refs.~\cite{Cutler:Fisher,Berti:Fisher,Poisson:Fisher}, this method relies on the crude assumption of Gaussian prior distributions\footnote{Typically, the more valid assumption is a uniform prior distribution; an improvement made in a more detailed Bayesian analysis.}.
The resulting posterior distribution is Gaussian with root-mean-sqaure given by:
\begin{equation}
\Delta \theta^a=\sqrt{\Big( \tilde{\Gamma}^{-1}\Big)^{aa}}.
\end{equation}
Here, the Fisher matrix $\tilde{\Gamma}$ is defined by:
\begin{equation}
\tilde{\Gamma}_{ab} \equiv \Big( \frac{\partial h}{\partial \theta^a} \Big| \frac{\partial h}{\partial \theta^a}\Big) + \frac{1}{\sigma_{\theta^a}^2} \delta_{ab}
\end{equation}
where $h$ is the waveform template, $\sigma_{\theta^a}$ is the parameters' prior root-mean-square estimate, and the inner product is defined by:
\begin{equation}
(a|b) \equiv 2 \int^{\infty}_0\frac{\tilde{a}^*\tilde{b}+\tilde{b}^*\tilde{a}}{S_n(f)}df.
\end{equation}
Lastly, $S_n(f)$ is the spectral noise density for the given interferometer.

We begin by authenticating this approach by applying a Fisher analysis to GW170817, as observed by LIGO with O2 detector sensitivity\zc{cite}.
Further, we scale the luminosity distance such that $SNR=32.4$, as was found in GW170817.
We also assume low spin priors $|\chi| \leq 0.05$, as well as $\tilde{\Lambda} \leq 3000$ and $|\delta \tilde{\Lambda}| \leq 500$~\cite{Wade:LambdaPriors}.
The resulting posterior distribution on $\tilde{\Lambda}$ has a range of $\pm 276.99$ encompassing the $90\%$ credible levels.
We compare these results with the Bayesian analysis performed in Ref.~\cite{TheLIGOScientific:2017qsa,Abbott2018}, finding close agreement with the resulting $90\%$ credible region of $70 \leq \tilde{\Lambda} \leq 720$.
This confirms the approximate validity of this method, allowing a continuation of this analysis for future detectors.

Next, we consider events identical to GW170817 detected on future design sensitivity upgrades and detectors aLIGO, a\texttt{++}, Voyager, CE, and ET\zc{cite} to determine if and when the statistical errors associated with parameter extraction of $\tilde{\Lambda}$ drop below the systematic EoS variation errors from using binary Love universal relations.
The process we use for each detector sensitivity $S_n^{\text{det}}(f)$ is as follows:
\begin{itemize}
\item Perform a Fisher analysis as outlined above using $S_n^{\text{det}}(f)$, while restricting the luminosity distance $D_L$ such that $SNR_{\text{O2}}=32.4$ would be achieved on O2 sensitivity $S_n^{\text{O2}}(f)$.
This results in statistical error $\sigma_1^{\text{det}}$ accrued in the extraction of $\tilde{\Lambda}$.
\item Generate a population of $N_{\text{det}}$ events corresponding to the expected binary NS merger detection rate, following the distribution $f=3 SNR_{\text{th}}^3/SNR^4$~\cite{Shutz:SNR,Chen:SNR} with a network SNR threshold of 8.
We approximate this to be proportional to the cube of SNR ratios over 2 observing runs: $N_{\text{det}} \sim N_{\text{O2}} (SNR_{\text{det}}/SNR_{\text{O2}})^3$, where $N_{\text{O2}}=2$, giving the rates shown in Table~\ref{tab:variances}.
\item Compute the population standard deviation given by:
\begin{equation}
\frac{1}{(\sigma_N^{\text{det}})^2}=\sum_i^{N_{\text{det}}}\frac{1}{(\sigma_i^{\text{det}})^2},
\end{equation}
where $\sigma_i^{\text{det}}$ is computed by the relations $\sigma_i^{\text{det}} \times SNR_i^{\text{det}} = \sigma_1^{\text{det}} \times SNR_1^{\text{det}}$.
\end{itemize}
The results are compiled in Table~\ref{tab:variances}, and shown graphically in Fig.~\ref{fig:stackedFisher} where $\sigma_1$ and $\sigma_N$ are plotted as a function of $SNR_1$ (the SNR as if GW170817 were detected on a future detector) for 5 future detector sensitivities.

\begin{table}[ht!]
\centering
\caption{
Tabulated results for the estimated statistical errors on $\tilde{\Lambda}$ for the combined results of $N_{\text{det}}$ detections corresponding to the estimated binary NS merger detection rate.
This is repeated for 5 future detector sensitivities: aLIGO, a\texttt{++}, Voyager, CE, and ET.
Below, $SNR_1$ and $\sigma_1$ correspond to the approximate SNR and $\sigma_{\tilde{\Lambda}}$ of GW170817 had it been observed by the future interferometer, and $\sigma_N$ corresponds to the final uncertainty on $\tilde{\Lambda}$ after $N_{\text{det}}$ detections.
It can be seen here that the statistical errors on $\tilde{\Lambda}$ become comparable with the systematics $\sigma_{\tilde{\Lambda}}=10$ from using improved binary Love relations from Voyager and on, indicating when it may be safe to utilize new universal relations.
Note the approximation for $\sigma_N$ under the O2 detector sensitivity is a poor estimate due to the small number of stacked events, $N_{\text{O2}}=2$, resulting in a high degree of randomness in population generation.
These results are shown graphically in Fig.~\ref{fig:stackedFisher}.
}\label{tab:variances}
\begin{tabular}{ c || c  c  c c } 
\hline
Detector & $N_{\text{det}}$ & $SNR_1$ & $\sigma_1$ & $\sigma_N$\\
\hline
\hline
O2 & $2$ & $32.40$ & $168.40$ & $425.53$\\
aLIGO & $44$ & $90.74$ & $75.44$ & $63.03$\\
a\texttt{++} & $355$ & $180.95$ & $31.55$ & $24.22$\\
Voyager & $4818$ & $428.89$ & $16.69$ & $7.78$\\
CE & $256620$ & $1398.03$ & $4.85$ & $0.97$\\
ET & $1349917$ & $2807.45$ & $6.26$ & $1.10$\\
\hline
\end{tabular}
\end{table}

>>>>

%Final Results
Upon use of the constrained set of EoSs, we find an improvement in binary Love universality by a factor of 25\% for stars with mass below 1.7 solar masses, and in I-Love-Q universality by a factor of 22\%.
Unfortunately, due to the current limitations in detector sensitivity, the systematic errors arising from EoS variation in the universal relations are far outweighed by the statistical errors accrued by extraction of high-order PN tidal parameters from GW waveforms.
Fig.~\ref{fig:stackedFisher} compiles the results from Fisher analyses approximating the uncertainties accrued from parameter extraction for GW170817 as if it had been observed by future detectors $A \equiv ($ O2, aLIGO, a\texttt{++}, Voyager, ET, CE$)$\zc{cite these individually}.
Here, $\sigma^A_{\text{GW170817}}$ and $\rho^A_{\text{GW170817}}$ correspond to the statistical error and signal-to-noise-ratio found from observing GW170817 on detector $A$, and $\sigma^A_N$ represents the combined uncertainty after the detection of $N_A$ events (corresponding to the binary NS merger rate associated interferometer $A$).
These values are further tabulated in Table~\ref{tab:variances}.
It can be seen from this figure that the statistical errors from parameter extraction become comparable the universal relation systematics (indicated by the magenta horizontal line) for the Voyager telescope - indicating when improved binary Love universal relations will become viable.
\begin{figure}
\begin{center} 
\includegraphics[width=\columnwidth]{stackedFisher.pdf}
\end{center}
\caption{
\zc{Redo this image in xmgrace.}
Estimated statistical uncertainties $\sigma^A_{\text{GW170817}}$ (blue) in the extraction of $\tilde{\Lambda}$ from GW170817 (O2) as if observed with future interferometers aLIGO, a++, Voyager, CE, and ET-D as a function of the signal-to-noise-ratio $\rho^A_{\text{GW170817}}$.
This is compared to the combined uncertainty $\sigma^A_N$ (orange) from the observation of multiple events from a simulated population of size $N_A$ corresponding to the expected rate of binary NS observations for O2, aLIGO, a\texttt{++}, Voyager, CE, and ET-D over 1 observing run: 1, 22, 177, 2409, 128310, and 674958 respectively.
It can be seen that the statistical errors in parameter extraction become comparable to the systematics from EoS variation in binary Love relations (magenta) for Voyager and on.
Note the approximation for $\sigma^A_N$ under the O2 detector sensitivity is a poor estimate due to the small number of stacked events, $N_{\text{O2}}=1$, resulting in a high degree of randomness in population generation.
These results are further tabulated in Table~\ref{tab:variances}.
}
\label{fig:stackedFisher}
\end{figure}

@@

In the current analysis, we consider only EoSs which have been constrained by the recent binary neutron star merger event, GW170817.
Important recent work~\cite{LIGO:posterior} uniformly sampled EoS parameters in order to derive a marginalized posterior on the pressure as a function of mass density, as seen in Fig. 2 of~\cite{LIGO:posterior}.
In our work, we similarly sample spectral coefficients within the ranges: $\gamma_0 \in \lbrack 0.2,2 \rbrack$, $\gamma_1 \in \lbrack -1.6,1.7 \rbrack$, $\gamma_2 \in \lbrack -0.6,0.6 \rbrack$, $\gamma_0 \in \lbrack -0.02,0.02 \rbrack$, and further restricting the adiabatic index to be $\Gamma \in \lbrack 0.6,4.5 \rbrack$, ensuring our parameterization exposes a wide range of viable EoSs~\cite{Lindblom:parameters}.
In addition, we impose similar constraints as was done in~\cite{LIGO:posterior}: (i) causality within 10\%, and (ii) EoS priors must support NS masses up to $1.97 \text{ M}_{\odot}$, consistent with astrophysical observations.
We then utilize the posterior defined by GW170817 by rejecting any EoS sample which does not lie within the 90\% credible posterior region, resulting in a sample of 35 EoSs shown in Fig.~\ref{fig:eos}.
Following~\cite{Read2009}, the parameterized high-density core EoSs generated above are matched to the low-density crust EoS Sly~\cite{Douchin:2001sv} at the density such that the pressures are equal.
For comparison, we also include a second sample of randomly generated EoSs, without restricting to GW170817s posterior.
\begin{figure}
\begin{center} 
\includegraphics[width=\columnwidth]{EoSs.pdf}
\end{center}
\caption{
\zc{Redo this image in xmgrace.}Set of 35 randomly generated EoSs used in our analysis. 
These were populated by uniformly sampling the spectral coefficient parameter space, then restricting to the 90\% credible level on EoS as derived by~\cite{LIGO:posterior}.
In addition, the following constraints were also applied: (i) the EoS must have a causal structure within 10\%, and (ii) the EoS must support maximum NS mass of at least $1.97 \text{ M}_{\odot}$, consistent with astrophysical observations.
}
\label{fig:eos}
\end{figure}

\subsection{Neutron Star Tidal deformability}\label{tidal}
Binary neutron star mergers, such as GW170817, provide valuable insight into the internal structure of such stars. 
Namely, tidal effects which enter the gravitational waveform depend strongly on the EoS defining the NSs structure. 
The ($l=2$ electric type) \emph{tidal deformability}, denoted as $\lambda$, has the largest impact on the waveform phase. 
Consider a NS of mass $M$ in the presence of the tidal field $\varepsilon_{ij}$ of a companion star.
In response, the NS will deform away from sphericity under the aquisition of quadrupole moment $Q_{ij}$, characterized by $\lambda$ as the linear response to $\varepsilon_{ij}$~\cite{Flanagan2008,hinderer-love,Yagi2013}:
\begin{equation}
Q_{ij}=-\lambda \varepsilon_{ij}.
\end{equation}
One can extract $Q_{ij}$ and $\varepsilon_{ij}$ -- and thus $\lambda$, or its dimensionless form $\Lambda \equiv \lambda/M^5$ -- via diffent asymptotic limits of the gravitational potential:
\begin{align}
\begin{split}
\Phi=\frac{1+g_{tt}}{2}&=-\frac{M}{r} - \frac{3}{2}\frac{Q_{ij}}{r^3} \Bigg(\frac{x^i}{r} \frac{x^j}{r}-\frac{1}{3}\delta_{ij} \Bigg) + \mathcal{O} \Bigg( \frac{M^4}{r^4} \Bigg)\\
&+ \frac{1}{2} \varepsilon_{ij} x^i x^j + \mathcal{O} \Bigg( \frac{r^3}{M^3} \Bigg).
\end{split}
\end{align}
The metric component $g_{tt}$ is determined by first constructing a spherically symmetric, non-spinning background solution, followed by the introduction of a perturbative tidal deformation.
Next, the perturbed Einstein equations must be solved in the NSs interior given an EoS, then matched to the exterior Schwarzschild solution at the surface, modulo a constant.
This process is described in more detail in Ref.~\cite{hinderer-love}.
Further, the stellar mass and radius are determined from $p(R)=0$, and the above mentioned constant.
Similarly, the moment of inertia is obtained from the asymptotic behavior of the $g_{t \phi}$ metric component.

Next, we consider the case of two NSs in a binary, such as the system found in GW170817, where each star 
individually experiences a neighboring tidal field.
Thus each star possesses tidal deformabilities $\Lambda_1$ and $\Lambda_2$ entering the gravitational waveform.
Due to strong correlations between these parameters, individual extraction is very difficult with current interferometer sensitivity limitations.
However, the waveform templates can be strategically reparameterized to instead include independant linear combinations of $\Lambda_1$ and $\Lambda_2$ to mitigate correlations between them. 
Any set of two independent functions may be used, for example: tidal parameters $\tilde{\Lambda}=\tilde{\Lambda}(\Lambda_1,\Lambda_2)$ and $\delta \tilde{\Lambda}=\delta \tilde{\Lambda}(\Lambda_1,\Lambda_2)$~\cite{Wade:tidalCorrections} first enter the gravitational waveform at 5PN and 6PN orders respectively, thus partially breaking degeneracies.
Here, $\tilde{\Lambda}$ is known as the mass weighted tidal deformability, or \emph{chirp deformability} due to its status as the dominant tidal parameter in the waveform.

@@

\subsection{I-Love-Q relations}\label{sec:ilq}
Here we present our results on I-Love-Q universality as compared to Fig. 1 of Yagi \textit{et al.}~\cite{Yagi:ILQ}.
Following this work, the data for each universal relation is fit to the following curve:
\begin{equation}\label{eq:ILQfit}
\ln{y_i}=a_i+b_i \ln{x_i} + c_i (\ln{x_i})^2 + d_i (\ln{x_i})^3 + e_i (\ln{x_i})^4,
\end{equation}
where the updated coefficients are given in Table~\ref{tab:ILQfit}.
In particular, we focus only on the I-Love universal relation for brevity, noting that the remaining relations Q-Love and I-Q show similar results.

@@

%%%%%%%%%%%%%%%%%%%%%%%%% Begin Future Observations %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Impact on future observations}\label{sec:observations}
In this section, we estimate the feasibility of ultilizing improved universal relations in future binary NS merger events.
This estimate is aqcuired through a simple Fisher analysis~\cite{Finn:Fisher,Cutler:Fisher} which approximates the accuracy with which one can extract best-fit parameters $\theta^a$, given a prior template waveform.
For the remainder of the paper, we consider a template parameter vector consisting of:
\begin{equation}
\theta^a=(\ln{A},\phi_c,t_c,\ln{\mathcal{M}},\ln{\mathcal{\eta}},\chi_s,\chi_a,\tilde{\Lambda},\delta \tilde{\Lambda}),
\end{equation}
where $A \equiv \sqrt{\frac{2 \eta}{3 \pi^{1/3}}}$ is a normalized amplitude factor, $\eta \equiv m_1 m_2/M^2$ is the symmetric mass ratio with $m_{1,2}$ and $M$ being the individual and total masses, $\mathcal{M}=M \eta^{3/5}$ is the chirp mass, and $\chi_{s,a}=\frac{1}{2}(\chi_1+\pm\chi_2)$ are the symmetric and antisymmetric total spins, where $\chi_{1,2}$ are the NSs individual spins. 
Following Refs.~\cite{Cutler:Fisher,Berti:Fisher,Poisson:Fisher}, this method relies on the crude assumption of Gaussian prior distributions\footnote{Typically, the more valid assumption is a uniform prior distribution; an improvement made in a more detailed Bayesian analysis.}.
The resulting posterior distribution is Gaussian with root-mean-sqaure given by:
\begin{equation}
\Delta \theta^a=\sqrt{\Big( \tilde{\Gamma}^{-1}\Big)^{aa}}.
\end{equation}
Here, the Fisher matrix $\tilde{\Gamma}$ is defined by:
\begin{equation}
\tilde{\Gamma}_{ab} \equiv \Big( \frac{\partial h}{\partial \theta^a} \Big| \frac{\partial h}{\partial \theta^a}\Big) + \frac{1}{\sigma_{\theta^a}^2} \delta_{ab}
\end{equation}
where $h$ is the waveform template, $\sigma_{\theta^a}$ is the parameters' prior root-mean-square estimate, and the inner product is defined by:
\begin{equation}
(a|b) \equiv 2 \int^{\infty}_0\frac{\tilde{a}^*\tilde{b}+\tilde{b}^*\tilde{a}}{S_n(f)}df.
\end{equation}
In this analysis, we consider the ``PhenomD" waveform template~\cite{PhenomDI,PhenomDII} modified by tidal corrections shown in Ref.~\cite{Wade:tidalCorrections}.
Lastly, $S_n(f)$ is the spectral noise density for the given interferometer.

We begin by authenticating this approach by applying a Fisher analysis to GW170817, as observed by LIGO with O2 detector sensitivity\zc{cite}.
Further, we scale the luminosity distance such that the signal-to-noise-ratio ($SNR \equiv \rho$) is fixed to be $\rho=32.4$, as was found in GW170817.
We also assume low spin priors $|\chi| \leq 0.05$, as well as $\tilde{\Lambda} \leq 3000$ and $|\delta \tilde{\Lambda}| \leq 500$~\cite{Wade:LambdaPriors}.
The resulting posterior distribution on $\tilde{\Lambda}$ has a range of $\pm 276.99$ encompassing the $90\%$ credible levels.
We compare these results with the Bayesian analysis performed in Ref.~\cite{TheLIGOScientific:2017qsa,Abbott2018}, finding close agreement with the resulting $90\%$ credible region of $70 \leq \tilde{\Lambda} \leq 720$.
This confirms the approximate validity of this method, allowing a continuation of this analysis for future detectors.
\begin{figure}
\begin{center} 
\includegraphics[width=\columnwidth]{sensitivities.pdf}
\end{center}
\caption{
\zc{redo this image in xmgrace}
Square root of of the spectral noise densities $\sqrt{S_n^A(f)}$ plotted for detectors ($A$): LIGO O2 (orange), aLIGO (green), a\texttt{++} (purple), Voyager (magenta), CE (red), and ET-D (blue) as interpolated from publicly available data\zc{cite}.
Spectral noise densities are plotted from $f_{\text{min}}=(23,10,10,7,1,1) \text{ Hz}$, respectively, to $f_{\text{max}}=1649 \text{ Hz}$.
Also shown is $2 \sqrt{f}$ multiplied by the amplitude of the PhenomD~\cite{PhenomDI,PhenomDII} waveform template, modified by tidal corrections from Ref.~\cite{Wade:tidalCorrections} used in our Fisher Analysis.
}
\label{fig:sensitivities}
\end{figure}

Next, we consider events identical to GW170817 detected on future design sensitivity upgrades and detectors $A \equiv ($O2, aLIGO, a\texttt{++}, Voyager, CE, ET-D$)$\zc{cite}, shown in Fig.~\ref{fig:sensitivities}, to determine if and when the statistical errors associated with parameter extraction of $\tilde{\Lambda}$ drop below the systematic EoS variation errors from using binary Love universal relations.
The process we use for each detector sensitivity $S_n^A(f)$ is as follows:
\begin{itemize}
\item Perform a Fisher analysis as outlined above using $S_n^A(f)$, while restricting the luminosity distance $D_L$ such that $\rho^{\text{O2}}_{\text{GW170817}}=32.4$ would be achieved on O2 sensitivity $S_n^{\text{O2}}(f)$.
This results in SNR $\rho^A_{\text{GW170817}}$ and statistical error $\sigma_\text{GW170817}^A$ accrued in the extraction of $\tilde{\Lambda}$ on detector $A$.
\item Generate a population of $N_A$ events corresponding to the expected binary NS merger detection rate for detector $A$, following the distribution $f=3 \rho_{\text{th}}^3/\rho^4$~\cite{Shutz:SNR,Chen:SNR} with a network SNR threshold of $\rho_{\text{th}}=8$.
We approximate this rate to be proportional to the cube of SNR ratios over 1 observing run: $N_A = N_{\text{O2}} (\rho^A_{\text{GW170817}}/\rho^{\text{O2}}_{\text{GW170817}})^3$, where $N_{\text{O2}}=1$, giving the rates shown inthe second column of Table~\ref{tab:variances}.
\item Compute the population standard deviation given by:
\begin{equation}
\frac{1}{(\sigma_N^A)^2}=\sum_i^{N_A}\frac{1}{(\sigma_i^A)^2},
\end{equation}
where $\sigma_i^A$ is computed by the relations $\sigma_i^A \times \rho_i^A = \sigma_{\text{GW170817}}^A \times \rho_{\text{GW170817}}^A$.
\end{itemize}
The results are compiled in Table~\ref{tab:variances}, and shown graphically in Fig.~\ref{fig:stackedFisher} where $\sigma^A_{\text{GW170817}}$ and $\sigma^A_N$ are plotted as a function of $\rho^A_{\text{GW170817}}$ (the SNR as if GW170817 were detected on future detector $A$) for 5 future detector sensitivities.

\begin{table}[ht!]
\centering
\caption{
Tabulated results for the estimated statistical errors on $\tilde{\Lambda}$ for the combined results of $N_A$ detections corresponding to the estimated binary NS merger detection rate.
This is repeated for 5 future detector sensitivities: aLIGO, a\texttt{++}, Voyager, CE, and ET.
Below, $\rho^A_{\text{GW170817}}$ and $\sigma^A_{\text{GW170817}}$ correspond to the approximate SNR and $\sigma_{\tilde{\Lambda}}$ of GW170817 had it been observed by the future interferometer, and $\sigma^A_N$ corresponds to the final uncertainty on $\tilde{\Lambda}$ after $N_A$ detections on interferometer $A$.
It can be seen here that the statistical errors on $\tilde{\Lambda}$ become comparable with the systematics $\sigma_{\tilde{\Lambda}}=10$ from using improved binary Love relations from Voyager and on, indicating when it may be safe to utilize new universal relations.
Note the approximation for $\sigma^A_N$ under the O2 detector sensitivity is a poor estimate due to the small number of stacked events, $N_{\text{O2}}=1$, resulting in a high degree of randomness in population generation.
These results are shown graphically in Fig.~\ref{fig:stackedFisher}.
}\label{tab:variances}
\begin{tabular}{ c || c  c  c c } 
\hline
Detector ($A$) & $N_A$ & $\rho^A_{\text{GW170817}}$ & $\sigma^A_{\text{GW170817}}$ & $\sigma^A_N$\\
\hline
\hline
O2 & $1$ & $32.40$ & $168.40$ & $314.90$\\
aLIGO & $22$ & $90.74$ & $75.44$ & $70.37$\\
a\texttt{++} & $177$ & $180.95$ & $31.55$ & $27.96$\\
Voyager & $2409$ & $428.89$ & $16.69$ & $10.21$\\
CE & $128310$ & $1398.03$ & $4.85$ & $1.39$\\
ET-D & $674958$ & $2807.45$ & $6.26$ & $1.53$\\
\hline
\end{tabular}
\end{table}
